---
title: "Descriptive Statistics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

<b>Normal Distribution</b>
<a href='https://www.tutorialspoint.com/r/r_normal_distribution.htm'>Documentation</a>
Generate a normal distribution
```{r}
mu <- 10
sd <- 2
norm_dist <- rnorm(100, mu, sd)
hist(norm_dist, main='Normal Distribution')
```

Plot the probability of different values in a normal distribution (with given mu and sd)
```{r}
nums <- seq(1,50, by=1)
probs <- dnorm(nums, mu, sd)
plot (nums, probs, type='l')
```

Find the probability of a normal distributed random number which follows a distribution of mu and sigma to be less than 10.
```{r}
random_num <- 10
prob <- pnorm(random_num, mu, sd)
print (prob)
```

Find the probability of a list of normal distributed random numbers which follow a distribution of mu and sigma to be less than 10.
```{r}
random_nums <- seq(-20,20,by=0.5)
probs <- pnorm(random_nums, mu, sd)
plot (random_nums, probs, type='l')
```

Find a number from a normal distribution (with mu and sd) whose probability is some given value
```{r}
prob <- 0.9
random_num <- qnorm(prob)
print (random_num)
```

<b>Binomal Distribution</b>
<a href='https://www.tutorialspoint.com/r/r_binomial_distribution.htm'>Documentation</a>
<br/>

Generate a Binomial Distribution
```{r}
num_success <- 50
num_trials <- 100
prob_succ <- 0.8
rbinom(num_success, num_trials, prob_succ)
```

Since binomial distribution is for discrete random variables we can generate pmf for binomial distribution for a given number of trials (num_trials) & success probability (prob_succ)
```{r}
num_success <- seq(1,100, by=1)
binom_dist <- dbinom(num_success, num_trials, prob_succ)
plot (num_success, binom_dist, type='l')
```
<b>POisson Distribution</b>
<a href='https://www.tutorialspoint.com/r/r_poisson_distribution.htm'>Documentation</a>
<br/>

Generate a Poisson Distribution
```{r}
lambda <- 100
rpois(100, lambda)
```

Since poisson distribution gives discrete random variables we can generate pmf for such distribution with a given lambda
```{r}
random_nums <- seq(1,60, by=1)
pois_dist <- dpois(random_nums, lambda = lambda)
plot (random_nums, pois_dist, type='l')
```

Show sample mean follows normal distribution if sample is selected from normal/binomal/poisson distribution